### 2016-09-30 assumptions.tex
Use "integer" instead of "integral" (same word the assumptions system uses)

The assumptions system allows users to specify that symbols have certain
common mathematical properties, such as being positive, imaginary, or
integral. SymPy is careful to never perform simplifications on an expression
unless the assumptions allow them. For instance, the identity $\sqrt{t^2} = t$
holds if $t$ is nonnegative ($t\ge 0$). However, for general complex $t$, no
such identity holds.

>>>>

The assumptions system allows users to specify that symbols have certain
common mathematical properties, such as being positive, imaginary, or
integer. SymPy is careful to never perform simplifications on an expression
unless the assumptions allow them. For instance, the identity $\sqrt{t^2} = t$
holds if $t$ is nonnegative ($t\ge 0$). However, for general complex $t$, no
such identity holds.
